manuscript_analysis_clean

### 2021-07-22 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd

## RT Model that has isSingular Warning:
```{r}
# isSingular Warning:
lmer_slope_m1 <-
  lmer(
    scaled_rt ~ group*targ_index*domain*modality + (1+domain+modality|id),
    # + (0 + (modality + domain) | id),
    data = rt_trial_scaled,
    contrasts = list(
      group = c(-0.5, 0.5),
      modality = c(-0.5, 0.5),
      domain = c(-0.5, 0.5)
    ),
    control=lmerControl(optimizer = "bobyqa")
  )
summary(lmer_slope_m1)

@@

## Trying Other RT Models:
```{r}
# Using raw reaction time and controlling for mean reaction time (isSingular Warning; Scaling issues)
lmer_slope_m2 <-
  lmer(reaction_time~group*targ_index*domain*modality + mean_rt + (1+domain+modality| id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5))
      )

@@

head(compositeAgeLNscaled)
```
## SL Cross-sectional Development Analyses: Younger group model has isSingular Warnings
```{r}
# Rescaling in each age group:
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]
compositeOldL$composite_score <- scale(compositeOldL$composite_score)

@@

# Younger group has isSingular Warnings
age_composite_m3 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeYoungL,
     contrasts = list(domain = c(-0.5, 0.5),
                      group = c(-0.5, 0.5))
     )

>>>>

## RT Model:
```{r}
lmer_slope_m1 <-
  lmer(
    scaled_rt ~ group*targ_index*domain*modality + (1+domain+modality|id),
    # + (0 + (modality + domain) | id),
    data = rt_trial_scaled,
    contrasts = list(
      group = c(-0.5, 0.5),
      modality = c(-0.5, 0.5),
      domain = c(-0.5, 0.5)
    ),
    control=lmerControl(optimizer = "bobyqa")
  )
summary(lmer_slope_m1)

@@

## Trying Other RT Models:
```{r}
# Using raw reaction time and controlling for mean reaction time (Scaling issues)
lmer_slope_m2 <-
  lmer(reaction_time~group*targ_index*domain*modality + mean_rt + (1+domain+modality| id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5))
      )

@@

head(compositeAgeLNscaled)
```
## SL Cross-sectional Development Analyses:
```{r}
# Rescaling in each age group:
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]
compositeOldL$composite_score <- scale(compositeOldL$composite_score)

@@

# Younger group
age_composite_m3 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeYoungL,
     contrasts = list(domain = c(-0.5, 0.5),
                      group = c(-0.5, 0.5))
     )
